---
title: "GneresComparison"
output: html_notebook
---



```{r}
library(tidyverse)
```

```{r}
genres_data <- read_csv('musical_artist.genres.csv')
```

```{r}
genres_grouped <- genres_data %>%
  group_by(genre)

genre_rock<- genres_grouped %>%
  mutate(
    genre_category = case_when(
      str_detect(genre, "rock") | str_detect(genre, "Rock") ~ "Rock",
      str_detect(genre, "bebop") |  str_detect(genre, "Bebop") ~ "Bebop"
      str_detect(genre, "classical") |  str_detect(genre, "Calssical") ~ "Classical"
      str_detect(genre, "pop") |  str_detect(genre, "Pop") ~ "Pop"
      str_detect(genre, "blues") |  str_detect(genre, "Blues") ~ "Blues"
      str_detect(genre, "jazz") |  str_detect(genre, "Jazz") ~ "Jazz"
      str_detect(genre, "country") |  str_detect(genre, "Country") ~ "Country"
      str_detect(genre, "folk") |  str_detect(genre, "Folk") ~ "Folk"
      str_detect(genre, "bebop") |  str_detect(genre, "Bebop") ~ "Bebop"
    )
  )
  # filter(str_detect(genre, "rock") | str_detect(genre, "Rock"))
  
```




Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
